Why does female meiosis allow the opportunity for exploitation by selfish sperm? BETTER TITLE?

### 2013-09-15 writeup_and_notes/male_dependent_drive.tex
Yaniv comments through discussion on sat

%Since all alleles within an individual rely on individual survival and reproduction for evolutionary success, most of life in a diploid eukaryotic genome is harmonious.
%However, this harmony is incomplete, as in numerous cases an allele can benefit (in the short or long term) from taking advantage of its host.
Despite the apparent unity of the organism, occasionally alleles can
gain an evolutionary advantage at a cost to  individual fitness
\citep{Burt2006}, often by exploiting meiosis and gametogensis.
%A clear opportunity for this conflict arises during gametogenesis where alternative alleles are in direct competition for representation in the next generation.
Female meiosis, an asymmetric event in which only one of two alternate alleles
enters the  egg, with the others consigned to the polar body, \yb{particularly vulnerable to such exploitation}  \citep{Sandler1957,Pardo-ManuelDeVillena2001a}. 
%Female meiosis is particularly unfair, only one of the four products of meiosis becomes an egg, while the other threes are disgarded into polar bodies. 
An allele that biases female meiosis in its favor (i.e. a meiotic driver), may increase in frequency even if this driver entails a pleiotropic fitness cost \citep{Prout1973}, generating a genetic conflict between the success of the driver and organismal fitness.
%Alleles that can segregate into the egg more than half the time in heterozygotes, by exploiting asymmetries, 
%can potentially increase in frequency in the population (i.e. experiencing true meiotic drive).
%If such alleles have fitness consequences they are a source of genetic conflict, 
%and can become balanced in the population if their host in homozygotes 
%out weighs their ability to spread to spread through heterozygotes. 
Meiotic drivers observed in nature (in both plants
\citep{Buckler1999,Fishman2005,Fishman2008}, and animals
\citep{Agulnik1990,Wu2005,Pardo-ManuelDeVillena2001c}) highlight this
conflict -- the selfish benefits of drive and the associated
pleiotropic fitness costs sustain a balanced polymorphism
\citep{Prout1973}, 
and often generate on ongoing evolutionary escalation of drive suppressors and enhancers \citep{Dawe1996,Fishman2008}. 
%Such balanced drive systems can cause the subsequent evolution of linked enhancers of drive
%and of supressors of drive throughout the genome. 
%Indeed, the known polymorphic female meiotic drive systems (OM, maize knobs, IN, mimulus, others?) habor
%a great diversity of enhancers and supressors. 
The threat of meiotic drive to organismal fitness is potentially so
severe that it has been hypothesized that many basic properties of
meiosis and o\"{o}genesis, including the initial genome doubling in
meiosis I \citep{Haig1991}, arrested female meiosis
\citep{Mira1998}, centromere machinery \citep{MalikHenikoff}, and sex differences in the recombination rate \citep{Haig2010,Brandvain2012} have evolved to disrupt meiotic drive and enforce fairness.

It is therefore somewhat surprising that despite the intense evolutionary pressure on female meiosis to prevent meiotic drive, 
it is potentially open to sabotage by a virtual stranger -- a haploid sperm genome.
That is, in many animal species, the completion of female meiosis requires fertilization of the egg, 
and there is ample opportunity for interaction between the sperm and female meiotic machinery.
If, for example, an allele in sperm could facilitate meiotic drive by a genetically equivalent allele in a 
heteromorphic dyad, such an allele could presumably bias meiosis in its favor and rapidly spread through the population.
At first sight, it seems as although female meiosis is primed to be exploited by selfish sperm systems.  
\yb{Why then is the requirement of fertilization to complete female meiosis so ubiquitous? }

@@

%Why then is the requirement of fertilization to complete female meiosis so ubiquitous? 
It is certainly not the case that animals are mechanistically incapable of evolving past this requirement.
There is considerable variation in which stage of meiosis requires fertilization, and 
a number of animal clades (should we try and lower bound how many transitions?) have evolved
to allow the completion of female meiosis upon ovulation. 
%(Although even in these organisms female meiosis 
%may also be subjection to influence by sperm alleles, if the sperm arrives at the egg soon enough after 
%ovulation to influence meiosis.)

@@

Here, we develop population genetic models exploring the evolution of alleles in sperm that influence the outcome of female meiosis 
%In this article we explore through simple population genetic models the consequences of alleles that influence the outcome of female meiosis.
These models argue that it is actually surprisingly hard for the influence of sperm on the outcome of meiosis to drive sustained conflict. 
In fact, the interests of sperm and egg  genomes' are often aligned, as are both invested in the fate of the resultant zygote 
	(as was speculated for the In locus \citep{Pomiankowski1993}).
Therefore, there is little selective benefit to females in preventing sperm to influence female meioses,
	indeed features of meiosis may evolve that facilitate the interaction of sperm with female meiosis.

@@

%yb version
In the standard model of female meiotic drive, the driving allele at a balletic site is transmitted to the egg with probability  $d > \frac{1}{2}$, regardless of sperm genotype. 
To depict a case of a self-promoting (or `green-bearded') meiotic driver,  we modify this standard model such that the female meiotic driver is only effective when fertilized by a sperm carrying that allele (see Figure \ref{Eggsperm_2_allele_cartoon}).
We then identify the conditions under which this self propagating driver can spread, and if it drive the evolution of suppressors? 
We note that the timing of fertilization relative to female meiosis places another constrain ton $d$, 
	for example, if fertilization (and therefore, sperm dependent drive) takes place at MII (as in mammals),
	female drive requires an uneven number of crossovers between the centromere and the drive locus, 
	so $d$ is bounded to be $<0.75$?.
\yb{I THINK THIS ORDER IS A BIT BETTER, BUT STILL ``OFF'', perhaps this is a footnote, or in methods or something...}

@@

% YB VERSION
We first consider the situation where the driving allele is neutral in heterozygotes, 
	but deleterious in homozygotes (whose relative fitness is $1-s$).  
In this model, a standard meiotic driver can always invade because 
	when rare it occurs predominantly in heterozygotes and therefore it initially pays no fitness cost. 
However, a severe homozygotes fitness cost ($s>XXd$) prevents  
	drivers from fixing  \citep{Prout1973}, 
	and provides an opportunity for the
	evolution of drive suppressors  \citep{XX}, corresponding well to 
	empirical examples of female meiotic drive.

@@

%YB VERSION
In contrast to a traditional driver, which can drive but pay no fitness cost when rare, 
	our green-bearded driver drives by creating homozygotes, and therefore pays a fitness cost even when rare. 
To simply increase when rare, our sperm-dependent driver must overcome a homozygous fitness cost.
Therefore with a recessive fitness cost,
	the conditions allowing the invasion of our green-bearded driver 
 	are far more restrictive than those for a standard meiotic driver (see Figure \ref{Invasion_space}).

@@

%YB VERSION
When a deleterious recessive green-bearded driver does spread, 
	it spends much time at low frequency, because when rare it is unlikely to meet a complimentary sperm. 
However, once common, a green bearded driver spreads rapidly to fixation due to their
	positive frequency dependent behavior (Inset in Figure \ref{Invasion_space}).  PERHAPS COMPARE TO TRADITIONAL DRIVER IN THIS FIGURE
Unlike standard meiotic drive systems, polymorphism of a green-bearded driver cannot be sustained by a homozygous cost, 
	because it already overcame this cost just to enter the population.
The lack of a balanced polymorphism precludes the evolution of an allele that suppresses this form of meiotic drive.

@@

%YB VERSION
Inclusion of a heterozygous fitness cost (e.g. additivity) further constrains the evolution of a sperm-dependent driver. 
A  standard female  driver can invade from low frequency so long as drive in heterozygotes out weighs the fitness cost they suffer (XXX); 
	however, when at low frequency our sperm dependent driver pays the heterozygous fitness cost but rarely drives because it is rare in sperm.
Therefore, even very weak heterozygous fitness costs
	prevent the spread of a very rare green-bearded driver, unless its drive is very strong. 
With an additive cost, the dynamics of a green-bearded driver resembles that of an underdominant mutation (in that the system is bistable). 
Below a cutoff frequency the allele deterministically decreases in frequency 
	because it pays the  heterozygous fitness cost  but drives is ineffectively (see FigureS\ref{bistable_additive}). 
Above this frequency, the allele increases deterministically because the commonness of sperm carrying this allele 
	make drive effective enough to overcome the associated fitness cost.
%becayse heterozygote eggs are fertilized by sperm with our allele %sufficiently often to beat the costs. 
This bistability will  prevent sperm-dependent drivers from invading 	
	reasonably sized populations, and assures that if they do invade they will rapidly fix.

@@

%yb version
%trying to make the models above sound less silly
While the sperm allele  could plausible influence the outcome of female meiosis, the limited levels of gene expression in sperm 
	suggest that sperm may influence the outcome of female meiosis as a function a the diploid genotype that produced the sperm perhaps due to proteins and RNAs packed in the sperm.
Models where male genotype, rather than sperm haplotype, determines the outcome of female meiosis 
	seem to behave qualitatively to those based on the allele of the
	fertilizing sperm (see Supplementary Figures XXX and XXX).
	\yb{THIS IS NOW WRONG WE NEED TO THINK ABOUT HOW TO WRITE THIS}

@@

Given the difficulty that meiotic drive alleles that promote themselves
through sperm have entering the population, the speed at
which they fix if they do, \yb{and the absence of balanced polymorphisms at such loci,} it seems very unlikely that such alleles
could drive the evolution of female \yb{suppressors}.

@@

\subsection*{B) A more biologically realistic selfish sperm-egg haplotype system}
These self promoting alleles are somewhat biologically unrealistic as
we are hypothesizing a newly evolved allele  
that both drives in female meiosis and has the ability to influence that drive in sperm.
Perhaps it is more realistic to think that a female drive system first
evolves and is maintained as a polymorphism in the population. 
This can then allow another allele to appears that further facilitates
female meiotic drive through its action in the sperm.

Our sperm-acting allele will be best able to spread if it arises in very close
linkage with the initial meiotic drive system as then it could potentially
hitchhiking due to the additional drive it causes. Polymorphic transmission distortion systems
have often evolved complex sets of inversions to prevent their breakup
\citep{XXX}, so it is reasonable to assume that for some female drive
systems there may be a reasonably large mutational target allowing our
allele to arise in tight linkage. Assuming very tight linkage we can
model this system using a model with three alleles at the same
locus. The first two alleles ($A$ and $B$) consist of our ancestral non-driver and
our original driver allele. The third allele ($C$) is the 
combined haplotype of our driver allele and the fully linked
sperm-acting promotor of drive.
 See Figure
\ref{Eggsperm_3_allele_cartoon} for a simple schematic of this drive model.

The problem for our sperm-acting promoter of drive (the novel C
allele), is that in order to have had time to evolve our original
drive system ($B$) has to be trapped at drive-homozygote disadvantage selection balance. 
Our new allele has arisen on the drive background so it
suffers from the same disadvantage. 
Worse yet, when our new allele it is rare it is often not helping
itself drive in females but instead $B$ ($C$ sperm meeting $AB$ eggs).
As $C$ facilitiates $B$ these interactions will frequently form 
$BC$ heterozygote which suffers from the full
effect fitness costs as $BB$.

Sperm-acting selfing alleles are therefore at a profound disadvantage
in this scenerio, even more so than under the previous two allele model.
We have found no parameter range of this
three allele system that allows the selfish sperm-acting allele $C$ to
invade the population.

There are other types of sperm acting alleles that influence
female meiosis that can invade the population. 
In particular sperm-acting alleles that act to restore 
the fairness of meiosis in females can spread. 
We could imagine that these act by 
disrupting whatever mechanistic asymmetry in female meiotic segregation the
drive initially evolved to exploit \citep{Pardo-ManuelDeVillena2001a}.\\

If these sperm-acting disrupting alleles arise at unlinked loci or on
the $A$ background they can readily invade a population segregating
for the drive system ($AB$, see Figure ). The invasion of such allele
will lower the frequency of the original drive system (perhaps to zero)
and will spread to fixation if they do not carry strong fitness costs
(Figure \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}A). \\
%These alleles are the sperm-acting equivalent of female 
%supressor of drive.

Intriguingly these sperm-acting distrupting alleles can also spread
when they arise tightly linked to the original drive system (B), forming
an novel third allele/haplotype C (Figures \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}B). This new allele spreads
to displace the original drive system (B) as it benefits from drive
but by disrupting drive when it is in the sperm it forms
 the deleterious $BC$ and $CC$ combinations less often (than the
 analogous combinations for the $B$ allele). 
\gc{Do we mention the In and Om locus here or in the discussion as a
  potential e.g. Do we mention the fact that the frequency of these
  newly invade sperm dodging alleles can be lower than the original system?}\\

Finally given a system of a balanced meiotic drive system which avoid
its own ill effects through a sperm-based mechanism
, such as that depicted in Figure XX and XX, female-based modifiers 
can evolve that act to further facilitate the sperms action in
disrupting driver.

>>>>

%Since all alleles within an individual rely on individual survival and reproduction for evolutionary success, most of life in a diploid eukaryotic genome is harmonious.
%However, this harmony is incomplete, as in numerous cases an allele can benefit (in the short or long term) from taking advantage of its host.
Despite the apparent unity of the organism, occasionally alleles can
gain an evolutionary advantage at a cost to  individual fitness
\citep{Burt2006}, often by exploiting meiosis and gametogensis.
%A clear opportunity for this conflict arises during gametogenesis where alternative alleles are in direct competition for representation in the next generation.
Because only one of the four products of female meiosis is transmitted to the egg, female meiosis \yb{is particularly vulnerable to such exploitation}  \citep{Sandler1957,Pardo-ManuelDeVillena2001a}. 
%Female meiosis is particularly unfair, only one of the four products of meiosis becomes an egg, while the other threes are disgarded into polar bodies. 
An allele that biases female meiosis in its favor (i.e. a meiotic driver), may increase in frequency even if this driver entails a pleiotropic fitness cost \citep{Prout1973}, generating a genetic conflict between the success of the driver and organismal fitness.
%Alleles that can segregate into the egg more than half the time in heterozygotes, by exploiting asymmetries, 
%can potentially increase in frequency in the population (i.e. experiencing true meiotic drive).
%If such alleles have fitness consequences they are a source of genetic conflict, 
%and can become balanced in the population if their host in homozygotes 
%out weighs their ability to spread to spread through heterozygotes. 
Meiotic drivers observed in nature (in both plants
\citep{Buckler1999,Fishman2005,Fishman2008}, and animals
\citep{Agulnik1990,Wu2005,Pardo-ManuelDeVillena2001c}) highlight this
conflict -- the selfish benefits of drive and the associated
pleiotropic fitness costs sustain a balanced polymorphism
\citep{Prout1973}, 
and often generate on ongoing evolutionary escalation of drive suppressors and enhancers \citep{Dawe1996,Fishman2008}. 
%Such balanced drive systems can cause the subsequent evolution of linked enhancers of drive
%and of supressors of drive throughout the genome. 
%Indeed, the known polymorphic female meiotic drive systems (OM, maize knobs, IN, mimulus, others?) habor
%a great diversity of enhancers and supressors. 
The threat of meiotic drive to organismal fitness is potentially so
severe that many basic properties of
meiosis and o\"{o}genesis, including the initial genome doubling in
meiosis I \citep{Haig1991}, arrested female meiosis
\citep{Mira1998}, centromere machinery \citep{MalikHenikoff}, and sex differences in the recombination rate \citep{Haig2010,Brandvain2012} 
have perhaps evolved to disrupt meiotic drive and enforce fairness.

It is therefore somewhat surprising that despite the intense evolutionary pressure on female meiosis to prevent meiotic drive, 
it is potentially open to sabotage by a virtual stranger -- a haploid sperm genome.
That is, in many animal species, the completion of female meiosis requires fertilization of the egg \yb{CITE}, 
and there is ample opportunity for interaction between the sperm and female meiotic machinery \yb{CITE}.
If, for example, an allele in sperm could facilitate meiotic drive by a genetically equivalent allele in a 
heteromorphic dyad, such an allele could presumably bias meiosis in its favor and rapidly spread through the population.
At first sight, it seems as although female meiosis is primed to be exploited by selfish sperm systems.  
\yb{Why then is the requirement of fertilization to complete female meiosis so ubiquitous? }

@@

%Why then is the requirement of fertilization to complete female meiosis so ubiquitous? 
It is certainly not the case that animals are mechanistically incapable of \yb{circumventing} this requirement.
There is considerable variation in which stage of meiosis requires fertilization, and 
a number of animal clades (should we try and lower bound how many transitions?) have evolved
to allow the completion of female meiosis upon ovulation. 
%(Although even in these organisms female meiosis 
%may also be subjection to influence by sperm alleles, if the sperm arrives at the egg soon enough after 
%ovulation to influence meiosis.)

@@

Here, we develop population genetic models exploring the evolution of \yb{sperm influence on female meiotic drive}. 
%In this article we explore through simple population genetic models the consequences of alleles that influence the outcome of female meiosis.
These models show that \yb{sperm modifiers of female meiotic drive are unlikely to create a sustained conflict.} 
%These models argue that it is surprisingly hard for the influence of sperm on the outcome of meiosis to drive sustained conflict. 
In fact, the interests of sperm and egg  genomes' are often aligned, as are both invested in the fate of the resultant zygote 
	(as was speculated for the In locus \citep{Pomiankowski1993}).
Therefore, there is little selective benefit to females in preventing sperm to influence female meioses,
	indeed features of meiosis may evolve that facilitate the interaction of sperm with female meiosis.

@@

%yb version
In the standard model of female meiotic drive, \yb{the driver is one of two alleles, and in heterozygotes is transmitted to the egg} with probability  $d > \frac{1}{2}$, regardless of sperm genotype. 
To depict a case of a self-promoting (or `green-bearded') meiotic driver,  we modify this standard model such that the driver is only effective when fertilized by a sperm carrying that allele (see Figure \ref{Eggsperm_2_allele_cartoon}).
We then identify the conditions under which this self propagating driver can spread, and evaluate whether a driver of this form could 
	\yb{generate a sustained conflict favoring the evolution of suppressors}. 
We note that the timing of fertilization relative to female meiosis places another constraint on $d$, 
	for example, if fertilization (and therefore, sperm dependent drive) takes place at MII (as in mammals),
	female drive requires an uneven number of crossovers between the centromere and the drive locus, 
	so $d$ is bounded to be $<0.75$?.
\yb{I THINK THIS ORDER IS A BIT BETTER, BUT STILL ``OFF'', perhaps this is a footnote, or in methods or something...}

@@

% YB VERSION
We first consider a driving allele neutral in heterozygotes, 
	but deleterious in homozygotes (whose relative fitness is $1-s$).  
In this model, a standard meiotic driver can always invade because 
	when rare it occurs predominantly in heterozygotes and it therefore drives without a fitness cost. 
However, a severe homozygous fitness cost ($s>XXd$) prevents  
	drivers from fixing  \citep{Prout1973}, 
	providing an opportunity for the evolution of
	drive suppressors \citep{XX}, corresponding well to 
	empirical examples of female meiotic drive.

@@

%YB VERSION
In contrast to a traditional driver, which drives but pays no fitness cost as a rare deleterious recissive, 
	our green-bearded driver specifically creates homozygotes when driving, and therefore there is a drive-associated fitness cost even when rare. 
Our sperm-dependent driver must overcome this homozygous fitness cost simply to spread when rare.
Therefore with a recessive fitness cost,
	the conditions allowing the invasion of our green-bearded driver 
 	are far more restrictive than those for a standard meiotic driver (see Figure \ref{Invasion_space}).

@@

%YB VERSION
When a deleterious recessive green-bearded driver does spread, 
	it spends much time at low frequency, because when rare it is unlikely to meet a complimentary sperm. 
However, once common, a green-bearded driver spreads rapidly to fixation due to its
	positive frequency dependent behavior (Inset in Figure \ref{Invasion_space}).  \yb{PERHAPS COMPARE TO TRADITIONAL DRIVER IN THIS FIGURE} 
Unlike standard meiotic drive systems, a homozygous cost, cannot sustain polymorphism of a green-bearded driver, 
	because it already overcame this cost just to enter the population.
The lack of a balanced polymorphism precludes the evolution of an allele that suppresses this form of meiotic drive.

@@

%YB VERSION
Inclusion of a heterozygous fitness cost (e.g. additivity) further constrains the evolution of a sperm-dependent driver. 
In contrast to a  standard female  driver which can invade from low frequency so long as drive in heterozygotes outweighs the fitness cost they suffer (XXX); 
	when rare our sperm dependent driver pays the heterozygous fitness cost but only weakly drives because it is rare in sperm. 
This frequency independent fitness cost, and positive frequency dependent drive generates a bistable system. 
%Therefore, even very weak heterozygous fitness costs
%	prevent the spread of a very rare green-bearded driver, unless its drive is very strong. 
%With an additive cost, the dynamics of a green-bearded driver resembles that of an underdominant mutation (in that the system is bistable). 
Below a cutoff frequency the green-bearded driver deterministically decreases in frequency 
	because it pays the  heterozygous fitness cost  but drives ineffectively (see FigureS\ref{bistable_additive}). 
Above this frequency, the allele increases deterministically because the commonness of sperm carrying this allele 
	make drive effective enough to overcome the associated fitness cost.
%becayse heterozygote eggs are fertilized by sperm with our allele %sufficiently often to beat the costs. 
This bistability prevents sperm-dependent drivers from invading 	
	reasonably sized populations, and assures that if they do invade they will rapidly fix.

@@

%yb version
%trying to make the models above sound less silly
While an allele specifically active in sperm allele  could plausibly influence the outcome of female meiosis, the limited levels of gene expression in sperm 
	suggest that sperm may influence female meiosis as a function a the diploid genotype that produced the sperm (perhaps due to proteins and RNAs packed in the sperm).
Models where male genotype, rather than sperm haplotype, determines the outcome of female meiosis 
	seem to behave qualitatively to those based on the allele of the
	fertilizing sperm (see Supplementary Figures XXX and XXX).
	\yb{THIS IS NOW WRONG WE NEED TO THINK ABOUT HOW TO WRITE THIS}

@@

Given the difficulty that green-bearded meiotic drivers have entering the population, the speed at
which they fix if they do, \yb{and the absence of balanced polymorphisms at such loci,} it seems very unlikely that such alleles
could drive the evolution of female \yb{suppressors}.

@@

\subsection*{B) A more biologically realistic selfish sperm-egg haplotype system}
Above, we explored a model were a driver that drove in females when signaled by a complementary allele in sperm.  
This complicated pleiotropic effect, while plausible is somewhat unlikely. 
Here, we examine an alternative scenario (and more realistic) in which first a driver is at drive-viability equilibrium,
	and subsequently a sperm dependent modifier of drive tightly linked to this allele invades.
	\yb{COMMENT XXX This is unclear. I think invades is wrong, bc it doesn't invade.  I think also we need to say if further increases Drive from D to D+ XXX }
\yb{Assuming tight linkage between female driver and sperm modifier is consistent with the nature of well characterized meiotic drive systems 
	which are often maintained as polymorphic inversions with numerous linked modifiers (CITE).}
\yb{??In the SUPP we explore the dynamics of a sperm modifier of female drive unlinked to the female driver??} 
%somewhat surprising combination of pleiotropic effect
%These self promoting alleles are somewhat biologically unrealistic as
%we are hypothesizing a newly evolved allele  
%that both drives in female meiosis and has the ability to influence that drive in sperm.
%Perhaps it is more realistic to think that a female drive system first
%evolves and is maintained as a polymorphism in the population. 
%This can then allow another allele to appears that further facilitates
%	female meiotic drive through its action in the sperm. 
%Our sperm-acting allele will be best able to spread if it arises in very close
%linkage with the initial meiotic drive system as then it could potentially
%hitchhiking due to the additional drive it causes. Polymorphic transmission distortion systems
%have often evolved complex sets of inversions to prevent their breakup
%\citep{XXX}, so it is reasonable to assume that for some female drive
%systems there may be a reasonably large mutational target allowing our
%allele to arise in tight linkage. 
We represent this as a three allele system where $A$ and $B$ are the ancestral non-driver and driver alleles, 
	and allele $B'$ is the non-recombining haplotype of a driver allele and sperm-acting drive modifier. 
	We note that in this model, $B'$ modifies drive of $B$ and $B'$ alleles equally, see Figure \ref{Eggsperm_3_allele_cartoon} for a simple schematic of this drive model.

Because the sperm-acting drive promoter (the novel $B'$ haplotype) is introduced when the ancestral driver ($B$) is at drive-selection balance, 
	$B'$ will immediately suffer a homozygous fitness cost.  
%Our new allele has arisen on the drive background so it suffers from the same disadvantage. 
Worse yet, a novel $B'$ haplotype most often helps 
	the $B$  allele drive ($B'$ sperm meeting $AB$ eggs), simply because $B$ is initially more common than $B'$.
As $B'$ facilitates $B$ these interactions will frequently form 
	$BB'$ heterozygote which suffers from the full
	effect fitness costs as $BB$. 
%The problem for our sperm-acting promoter of drive (the novel $B'$ 
%allele), is that in order to have had time to evolve our original
%drive system ($B$) has to be trapped at drive-homozygote disadvantage selection balance. 
%Our new allele has arisen on the drive background so it
%suffers from the same disadvantage. 
%Worse yet, when our new allele it is rare it is often not helping
%itself drive in females but instead $B$ ($B'$ sperm meeting $AB$ eggs).
%As $B'$ facilitates $B$ these interactions will frequently form 
%$BB'$ heterozygote which suffers from the full
%effect fitness costs as $BB$. 
Sperm-acting self promoting alleles are therefore at a profound disadvantage
in this scenario, even more so than under the previous two allele model.
We have found no parameter range of this
three allele system that allows the selfish sperm-acting allele $B'$ to
invade the population. \yb{MATHS?}

While  sperm enhancement of a female drive cannot displace a polymorphic female driver, sperm based drive suppression - that is sperm-acting alleles that act to restore 
fairness of female meiosis can. 
%In particular sperm-acting alleles that act to restore 
%the fairness of meiosis in females can spread. 
%We could imagine that these act by 
%disrupting whatever mechanistic asymmetry in female meiotic segregation the
%drive initially evolved to exploit \citep{Pardo-ManuelDeVillena2001a}.\\
%There are other types of sperm acting alleles that influence
%female meiosis that can invade the population. 
%In particular sperm-acting alleles that act to restore 
%the fairness of meiosis in females can spread. 
%We could imagine that these act by 
%disrupting whatever mechanistic asymmetry in female meiotic segregation the
%drive initially evolved to exploit \citep{Pardo-ManuelDeVillena2001a}.\\
 If these sperm-acting drive suppressors arise on
	the $A$ background or are unlinked to the drive locus they readily invade a population segregating
for the drive system ($AB$, see Figure ). The invasion of such allele
will lower the frequency of the original drive system (perhaps to zero)
and will spread to fixation if they do not carry strong fitness costs
(Figure \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}A). \\
%These alleles are the sperm-acting equivalent of female 
%supressor of drive.
%If these sperm-acting disrupting alleles arise at unlinked loci or on
%the $A$ background they can readily invade a population segregating
%for the drive system ($AB$, see Figure ). The invasion of such allele
%will lower the frequency of the original drive system (perhaps to zero)
%and will spread to fixation if they do not carry strong fitness costs
%(Figure \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}A). \\
%These alleles are the sperm-acting equivalent of female 
%supressor of drive.

Intriguingly these sperm disruptors of female meiotic drive can spread
	even when they arise tightly linked to the original drive system (B), forming
	an novel third allele $B^*$ as above (Figures \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}B). 
$B^*$ displaces the original drive system ($B$) because it drives when not costly, 
	but by disrupting drive when transmitted to sperm it avoids low-fitness drive homozygotes ($BB^*$ and $B^*B^*$. 
Surprising despite displacing the ancestral driver ($B$), self avoiding driver, $B^*$ it's equilibrium frequency is not always higher than that of $B$. 
	% as it benefits from drive but by disrupting drive when it is in the sperm it forms the deleterious $BC$ and $CC$ combinations less often (than the  analogous combinations for the $B$ allele). 
\gc{Do we mention the In and Om locus here or in the discussion as a
	 potential e.g. Do we mention the fact that the frequency of these
	 newly invade sperm dodging alleles can be lower than the original system?}\\

Finally given a system of a balanced meiotic drive system which avoid
its own ill effects through a sperm-based mechanism
, such as that depicted in Figure XX and XX, female-based modifiers 
can evolve that act to further facilitate the sperms action in
disrupting driver. \yb{THIS SOUNDS MORE DISCUSSIVE}
